\documentclass[10pt,a4paper]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\usepackage{eurosym}
\usepackage[scale=0.75]{geometry}
%\usepackage[backend=biber,bibencoding=ascii,sorting=none,giveninits=true,maxnames=5]{biblatex}
%\bibliography{pubs}
%\DefineBibliographyStrings{english}{%
%  references = {Publications},
%}

% personal data
\name{Guillermo A.}{P\'erez}
\title{CV}
\address{Middelheimlaan 1}{2020 Antwerpen}{Belgium}
\phone{+3232653904}
\email{guillermo.perez@uantwerpen.be}
\homepage{www.uantwerpen.be/en/staff/guillermoalberto-perez/}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2012--2016}{Ph.D. Computer Science}{Universit\'e libre de Bruxelles
(ULB)}{Brussels, Belgium}{}{}
\cventry{2010--2012}{M.Sc. Information Systems and Applications}{National
Tsing-Hua University (NTHU)}{Hsinchu,
Taiwan}{}{}
\cventry{2005--2009}{B.Sc. Computer Science}{Universidad Tecnol\'ogica
Centroamericana (UNITEC)}{Tegucigalpa, Honduras}{\textbf{Summa cum Laude}}{}

\section{Awards and Scholarships}
\begin{itemize}
  \item Outstanding Paper Award -- AAAI Conf. on AI (AAAI) \hfill{2025}
  \item Best Paper Award -- Int'l Conf. on Formal Modeling
    \& Analysis of Timed Sys. (FORMATS) \hfill{2023}
  \item Outstanding Teaching Award within the Faculty of Science, University
    of Antwerp \hfill \textit{2021}
	\item Fondation Wiener-Anspach Post-Doctoral subsidy \hfill
		\textit{2017}
  \item Kurt G\"odel medal for my synthesis tool AbsSynthe at FLoC Olympic
    Games \hfill \textit{2014}
	\item Fonds de la Recherche Scientifique (F.R.S.-FNRS) Aspirant
		fellowship \hfill \textit{2014--2018}
  \item International Cooperation and Development Fund (ICDF) scholarship
    \hfill \textit{2010--2012}
\end{itemize}

\subsection{In the media}
My research, mostly in the context of formal methods for trustworthy AI, has
been featured in the media:
\begin{itemize}
  \item Our ``outstanding'' AAAI 2025 paper on a decidable class of partially
    observable Markov decision processes was the topic of two blog posts in Le
    Monde’s binaire and it was covered by AIhub.org
  \item Results from Dennis Groß’ 2020 collaboration with TNO on attacking models
    for image classification were featured in an article of NewScientist
\end{itemize}

\section{Employment}
\cventry{October 2023--present}{Tenured Associate Professor}{University
of Antwerp}{Antwerp, Belgium}{}{}
\cventry{October 2018--2023}{Tenure-Track Assistant Professor}{University
of Antwerp}{Antwerp, Belgium}{}{}
\cventry{January 2017--October 2018}{Research Assistant (supported by
F.R.S.-FNRS)}{Universit\'e libre de Bruxelles}{Brussels, Belgium}{}{}
\cventry{2017}{Visiting Researcher}{University
of Oxford}{Oxford, United Kingdom}{}{}
\cventry{2008--2010}{Software Engineer}{Inform\'atica
Atl\'antida}{Tegucigalpa, Honduras}{}{}

\section{Membership in Scientific Societies}
\cventry{2023--present}{Working with colleagues in Europe on formal methods
for and with artificial intelligence}{Member of ELLIS: European
Laboratory for Learning and Intelligent Systems}{Europe}{}{}
\cventry{2020--present}{The Flemish strategic research center for
the manufacturing industry}{Member of Flanders
Make core lab at the University of Antwerp}{Antwerp, Belgium}{}{}

\section{Languages}
\begin{minipage}[t]{.48\linewidth}
	\textbf{English:} Fluent\\
	\textbf{Dutch:} Fluent\\
	\textbf{Spanish:} Native
\end{minipage}
\hfill
\begin{minipage}[t]{.48\linewidth}
	\textbf{French:} Fluent\\
	\textbf{Mandarin Chinese:} Basic\\
	\textbf{German:} Basic
\end{minipage}

\section{Supervision}
\subsection{Post-doctoral researchers}
\begin{itemize}
  \item Dr. Marnix Suilen \hfill \textit{2024--present}
\end{itemize}

\subsection{PhD students}
\begin{itemize}
  \item K\'evin Dubrulle (with Prof. Bruy\`ere at UMons) \hfill
    \textit{2025--present}
  \item Vanessa Fl\"ugel (with Prof. Blondin at Sherbrooke) \hfill \textit{2025--present}
  \item Kasper Engelen \hfill \textit{2022--present}
\end{itemize}

\subsection{Alumni}
\begin{itemize}
  \item Dr. Ramesh Krishnamurthy (with Prof. Denil at UAntwerp) \hfill
    \textit{2021--2025}
  \item Dr. Shrisha Rao \hfill \textit{2021--2025}
  \item Dr. Ga\"etan Staquet (with Prof. Bruy\`ere at UMons) \hfill
    \textit{2020--2024}
  \item Dr. Tim Leys \hfill \textit{2020--2024}
  \item Dr. Florent Delgrange (with Prof. Now\'e at VUB) \hfill
    \textit{2020--2024}
  \item Dr. Dennis Gross (with Prof. Jansen at Radboud) \hfill
    \textit{2019--2024} 
  \item Dr. Ritam Raha (with Dr. Fijalkow at LaBRI, Bordeaux) \hfill
    \textit{2019--2023}
  \item Dr. Rapha\"el Berthon (with Prof. Raskin at ULB) \hfill
    \textit{2018-2022}
\end{itemize}

\section{Teaching and Service}
\subsection{Bachelor's courses taught at UAntwerp}
\begin{itemize}
  \item Theoretical Computer Science Seminar (2nd Sem.) \hfill
    \textit{2024--present}
  \item Compilers (1st Sem.) \hfill \textit{2019--present}
\end{itemize}

\subsection{Master's courses taught at UAntwerp}
\begin{itemize}
  \item Mathematical Foundations of Reinforcement Learning (1st Sem.) \hfill \textit{2021--present}
  \item Specification and Verification (1st Sem.) \hfill \textit{2019--present}
  \item Programming Paradigms (2nd Sem.) \hfill \textit{2019--present}
  \item Software Testing and Beyond Summer School \hfill \textit{2025--present}
\end{itemize}

\subsection{Service at UAntwerp}
\begin{itemize}
  \item Vice-chair of the Department of Computer Science \hfill
    \textit{2025--present}
  \item CS-Department Planning Manager for Students and
    Assistants Supporting Courses \hfill \textit{2025--present}
  \item Member of the Pre-Screening Commission for Int'l Masters'
    Programs in CS \hfill \textit{2018--present}
\end{itemize}

\section{Service to the Community}
\subsection{Selected invited talks}
\cventry{2025}{Annual Meeting of the Verification Working Group
(GT-V\'erif)}{Keynote: Proof Over Promises! Making RL
Trustworthy}{France}{}{}
\cventry{2025}{Competitions and Empirical Evaluations in Automated Reasoning - Dagstuhl
Seminar (25441)}{SYNTCOMP: The Reactive Synthesis Competition}{Germany}{}{}
\cventry{2025}{8th International Symposium on AI Verification (SAIV)}{Decidable
Problems for Partially Observable MDPs}{Croatia}{}{}
\cventry{2024}{Automated Synthesis: Functional, Reactive and Beyond - Dagstuhl
Seminar (24171)}{The Reactive Synthesis Competition (SYNTCOMP): 2018-2021}{Germany}{}{}
\cventry{2021}{10th International Workshop on Weighted Automata: Theory and
Applications}{Parameter Synthesis for One-Counter Automata}{France}{}{}
\cventry{2020}{International
Symposium on Games, Automata, Logics, and Formal Verification
(GandALF)}{Regret Minimization in Discounted-Sum Games}{Belgium}{}{}
\cventry{2020}{22nd International Workshop on Verification of Infinite-State Systems}{Revisiting Synthesis for One-Counter Automata}{Germany}{}{}
\cventry{2019}{Workshop: Theory and Algorithms in Graph and Stochastic Games}{Optimizing Expectation with Guarantees in POMDPs}{Belgium}{}{}
\cventry{2018}{Machine Learning and Model Checking Join Forces - Dagstuhl
Seminar (18121)}{Graph-Based Reductions for Model Checking and Learning
MDPs}{Germany}{}{}

\subsection{Competition organizer}
\cventry{2019--present}{SYNTCOMP is affiliated with the conference CAV, \url{https://www.syntcomp.org/}}{Annual Reactive Synthesis
Competition, with S. Jacobs, P. Schlehuber-Caissier}{}{}{}

\subsection{Steering committee member}
\begin{itemize}
  \item The International Conference on Quantitative Evaluation of SysTems
    (QEST) \hfill \textit{2023--2027}
\end{itemize}

\subsection{Program chair}
\begin{itemize}
  \item Organizer of the ``The Futures of Reactive Synthesis'' Dagstuhl
    seminar (23391), with N. Fijalkow, B. Finkbeiner, and E. Polgreen \hfill
    \textit{2023}
  \item General \& program chair of the Int'l Conf. on
    Concurrency (CONCUR) 2023, with J.-F. Raskin \hfill
    \textit{2023}
  \item Workshop chair of the Federated Logic Conference (FLoC) 2022, joint
    with S. Almagor \hfill \textit{2022}
  \item Program chair of the Workshop on Synthesis (SYNT 2021), joint
    with E. Polgreen \hfill \textit{2021}
  \item Organizer of SYNTCOMP Camp, a satellite tutorial of ETAPS 2019
    \hfill \textit{2019}
\end{itemize}

\subsection{Program committee member}
\begin{itemize}
  \item 52nd EATCS Int'l Colloquium on Automata, Languages, and
    Programming (ICALP 2026) \hfill \textit{2026}
  \item 32st Int'l Conf. on Tools \& Algorithms for the
    Construction \& Analysis of Systems (TACAS 2026) \hfill \textit{2026}
  \item 45th IARCS Conf. on Foundations of Software Tech. and
    Theoretical Comp. Sci. (FSTTCS 2025) \hfill \textit{2025}
  \item 11th Symposium on Dependable Software Eng. Theories, Tools and
    Applications (SETTA 2025) \hfill \textit{2025}
  \item 50th International Symposium on Mathematical Foundations of Computer
    Science (MFCS 2025) \hfill \textit{2025}
  \item 32nd EACSL Annual Conference on Computer Science Logic (CSL 2024)
    \hfill \textit{2024}
  \item 34rd Benelux Conf. on AI and the 31th
    Belgian Dutch Conf. on ML (BNAIC/BeNeLearn 2022) \hfill \textit{2022}
  \item 18th Conference on Formal Modeling and Analysis of Timed
    Systems (FORMATS 2020) \hfill \textit{2020}
  \item Int'l Conference on Autonomous Agents and Multi-Agent
    Systems (AAMAS) \hfill \textit{2024, 2026}
  \item Int'l Conference on Concurrency Theory (CONCUR) \hfill
    \textit{2024, 2026}
  \item Int'l Symposium on AI Verification (SAIV) \hfill
    \textit{2024, 2025}
  \item Int'l Conference on Applications and Theory of Petri Nets
    and Concurrency (PN) \hfill \textit{2024, 2025}
  \item AAAI Conference on Artificial Intelligence (AAAI) \hfill
    \textit{2021, 2022, 2023, 2026}
  \item Int'l Symp. on Games, Automata, Logics, and Formal
    Verif. (GandALF) \hfill \textit{2021, 2022, 2023, 2024}
  \item Conference on Reachability Problems (RP) \hfill \textit{2019, 2022,
    2025}
  \item Workshop on Synthesis (SYNT) \hfill \textit{2019, 2022, 2024, 2025}
\end{itemize}

\subsection{Other service}
\begin{itemize}
  \item Artifact Evaluation Chair for FoSSaCS 2026 \hfill \textit{2026}
  \item Part of the iCORE Ranking Application for QEST-FORMATS \hfill
    \textit{2025}
  \item Scientific Advisor of ReqCon.ai in ELSA-ai.eu Funded Project \hfill
    \textit{2025}
\end{itemize}

\section{Research Grants}
\cventry{2024--2027}{Funded by the Research Foundation - Flanders (FWO) at
UAntwerp}{PI of Synthesis of reactive systems from formal specifications and
examples (SynthEx)}{\euro 194K}{}{}
\cventry{2021--2024}{Funded by the Inter-university Research Fund (iBOF),
Flanders, Belgium}{co-PI of Infectious disease economics and AI with
guarantees
(DESCARTES)}{\euro 800K}{}{}
\cventry{2020--2023}{Funded by Flanders Make, the strategic research center
for the Flemish manufacturing industry}{co-PI of Deterministic and inexpensive
realizations of advanced control (DIRAC-SBO)}{\euro 468K}{}{}
\cventry{2020--2023}{Funded by the Research Foundation - Flanders (FWO) at
UAntwerp}{PI of Safe Artificial Intelligence and Learning for Verification
(SAILor)}{\euro 254K}{}{}
\cventry{2019--2023}{Funded by the University Research Fund (BOF) at
UAntwerp}{PI of Counter-Automata Algorithms for Software Verification Tools
(CAST)}{\euro 205K}{}{}

%\section{Software Tools}
%\begin{itemize}
%  \item \href{https://github.com/gaperez64/AbsSynthe}{AbsSynthe}: A
%    controller-synthesis tool from safety specifications
%  \item \href{https://github.com/gaperez64/GPOMCP}{GPOMCP}: A
%    partial-observation Monte Carlo planner with guarantees
%  \item \href{https://github.com/gaperez64/acacia-bonsai}{Acacia-bonsai}:
%    Universal coB\"uchi synthesis algorithms for temporal specifications
%\end{itemize}


%\section{References}
%\begin{cvcolumns}
%  \cvcolumn{}{%
%	  \begin{itemize}
%		  \item
%  Ann Now\'e, Ph.D.\\
%  Prof. at VUB, Belgium\\
%  Email: ann.nowe@vub.be
%  		  \item
%  Frits W. Vaandrager, Ph.D.\\
%  Prof. at Radboud University, Netherlands\\
%  Email: f.vaandrager@cs.ru.nl
%  	\end{itemize}
%  }
%  \cvcolumn{}{%
%	\begin{itemize}
%  		  \item
%  Joost-Pieter Katoen, Ph.D.\\
%  Prof. at RWTH Aachen University, Germany\\
%  Email: katoen@cs.rwth-aachen.de
%        \item
%  Jean-Fran\c{c}ois Raskin, Ph.D.\\
%  Prof. at Universit\'e libre de Bruxelles, Belgium\\
%  Email: jraskin@ulb.ac.be
%  	\end{itemize}
%  }
%\end{cvcolumns}
%
%\clearpage
%\nocite{*}

%\printbibliography

\end{document}
